---
title: "Assignment-Regression Analytics"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(Warning =  FALSE)
```

**1.**
```{r}
set.seed(2017) 
X=runif(100)*10 
Y=X*4+3.45 
Y=rnorm(100)*0.29*Y+Y 

```

**(a)Plot Y against X:**

```{r}
plot(Y~X)
```

*Based on the plot, it is clear that the value of Y keeps increasing with the value of X indicating that there is a positive correlation between X and Y. Hence, we can fit a linear model to explain Y based on X.*

\newpage
**(b) Simple linear model of Y based on X:**
```{r}
 linear_model<- lm(Y~X)
linear_model$coefficients

```
**Equation explaining Y based on X:**

$$Y = 3.61075* X +4.465490$$

**Accuracy of the model:**
```{r}

summary(linear_model)

```
*Considering R square value to predict the accuracy of the model as R square is the measure of performance of a linear Regression model. In this case, R square is 0.6517 indicates that the model is 65.17 percent accurate.*



**(c) How the Coefficient of determination R^2,of the model is related to the correlation coefficient of X and Y?**

```{r}
cor(Y,X)

```

*The correlation coefficient calculated above indicates that there is a positive correlation of 0.807291 between X and Y. Coefficient of determination is the square of this value.*

\newpage


**2**


**(a)**
```{r}
head(mtcars)

#constructing linear regression model to determine hp based on weight of the car:
linear_model1<- lm(hp~wt,data=mtcars)
summary(linear_model1)


#constructing linear regression model to determine hp based on Mile per Gallon(mpg) of the car:
linear_model2<-lm(hp~mpg,data=mtcars)
summary(linear_model2)

```

*To best determine which variable can be used to estimate the horse power of a car, we are considering R square value as it implies the proportion of variability of the dependent variable accounted for the independent variable.*


*R square value to estimate horse power based on weight is 43.39 percent whereas the R square value to estimate horse power based on miles per Gallon is 60.24 percent.*

*Therefore, it is clear to say that the horse power can be best estimated with the value of mpg and not based on the weight of the car.*

*Hence, Chris is right about estimating the horse power of the car*

**(b)Constructing a model to predict the car horse power based on number of cylinders and miles per Gallon:**

```{r}
linear_model3<- lm(hp~cyl+mpg,data = mtcars)
summary(linear_model3)

```
**Linear equation:**

$$ hp = 54.067+23.979 * X_1 -2.775*X_2 $$
$$where X_1 = cyl, X_2 = mpg$$
**Estimated horsepower of a car with 4 cylinders and mpg of 22:**
```{r}
predicted_hp_value<-predict(linear_model3,data.frame(cyl=c(4),mpg=c(22)))

predicted_hp_value
```
*The estimated horse power of a car with 4 cylinders and 22 mpg is 88.93618*

\newpage
**3**
**(a) building a model to estimate the median value of owner occupied homes based on crime rate, proportion of residential land zoned for lots over 25,000 sq.ft,the local pupil-teacher ratio (ptratio) and weather the whether the tract bounds Chas River:**
```{r}

library(mlbench)
data(BostonHousing)

linear_model4<-lm(medv~crim+zn+ptratio+chas,data=BostonHousing)

summary(linear_model4)

```
*The above model is 35.99 percent accurate which is a relatively low percent. Hence, we don't consider this as a good model*

**(b) Identifying which of the two identical houses is more expensive:**

*To identify which home is expensive comparing the one that bounds the Chas river and the one's do not, we consider the coefficient of the chas value in the above linear model. The coefficient is 4.58393, indicates that the houses that bounds by the Chas river are 4.58393 times more expensive than the houses which do not bounds by the river.*

*Moreover, in the dataset, the values of chas river are 1 or 0 which means the houses which bounds by the river are assigned a value of 1, otherwise 0. So for the houses which do not bounds by the river are going to have 0 times change in their value*


**(c) Finding which of the variables are statistically important:**

*All the variables including crime rate,proportion of residential land zoned for lots over 25,000 sq.ft,the local pupil-teacher ratio,the tract bounds Chas River are statistically important as all of them has very low P value*

**(d)Determining the order of importance of the 4 variables using ANOVA analysis:**

```{r}

anova_lm<-anova(linear_model4)
anova_lm

```
*The importance of variables can be determined by their Sum of Squares value. Higher the Sum of squares, the more important is the variable in estimating the value of a dependent variable*

*Order of importance of variables:*

*crim-per capita crime rate by town*

*ptratio-pupil-teacher ratio by town.*

*zn-proportion of residential land zoned for lots over 25,000 sq.ft.*

*Chas-Charles River dummy variable*






